### 2015-07-08 2015-compmorphon-morphver/poster.tex
updated dev cycle
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61219 72bbbca6-d526-0410-a7d9-f06f51895060

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			\scalebox{0.8}{
			\begin{tikzpicture}[node distance = 2cm, auto]
				% Place nodes
				\node [block] (init) at (1,3) {analyse corpus} ;
				\node [cloud, left of=init] (addstem) at (0,3) {add stem};
				\node [cloud, right of=init] (fixphon) at (2,3) {fix phonology};
				\node [block, below of=init] (freq) at (1,2) {examine frequency list};
				\node [decision, right of=freq] (break) at (1.5,0) {did something break?};
				%\node [block, below of=identify] (evaluate) {evaluate candidate models};
				%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
				\node [decision, below right of=freq] (decide) at (0,-1) {cause for unanalysed forms?};
				%\node [block, below of=decide, node distance=3cm] (stop) {stop};
				% Draw edges
				\path [line] (init) -- (freq);
				\path [line] (freq) -- (break);
				\path [line] (break.south) -| node [near start] {no} (decide.north) ;
				\path [line] (break.north) -| node [near start] {yes}(fixphon.south) ;
				\path [line] (decide) -| node [near start] {missing stem} (addstem);
				\path [line] (decide.east) --(decide-|fixphon.east) node [below, midway] {bad phonology} |-(break.north-|fixphon.south) -- (fixphon.south);
				\path [line,dashed] (addstem) -- (init);
				\path [line,dashed] (fixphon) -- (init);
			\end{tikzpicture}}
		}

>>>>

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			\scalebox{0.8}{
			\begin{tikzpicture}[node distance = 2cm, auto]
				% Place nodes
				\node [cloud, above of=fixphon] (assumed) at (5.5,1.5) {assumed phonology} ;
				\node [block] (init) at (1,3) {analyse corpus} ;
				\node [block, left of=init] (addstem) at (0,3) {add stem};
				\node [block, right of=init] (fixphon) at (3.5,3) {fix phonology};
				\node [block, below of=init] (freq) at (1,2) {examine frequency list};
				\node [decision, right of=freq] (break) at (1.5,0) {did something break?};
				%\node [block, below of=identify] (evaluate) {evaluate candidate models};
				%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
				\node [decision, below right of=freq] (decide) at (0,-1) {cause for unanalysed forms?};
				\node [cloud] (revised) at (6.75,-4.5) {revised phonology} ;
				%\node [block, below of=decide, node distance=3cm] (stop) {stop};
				% Draw edges
				\path [line] (init) -- (freq);
				\path [line] (freq) -- (break);
				\path [line] (break.south) -| node [near start] {no} (decide.north) ;
				\path [line] (break.north) -| node [near start] {yes}(fixphon.south) ;
				\path [line] (decide) -| node [near start] {missing stem} (addstem);
				\path [line] (decide.east) --(decide-|fixphon.east) node [below, midway] {bad phonology} |-(break.north-|fixphon.south) -- (fixphon.south);
				\path [line] (addstem) -- (init);
				\path [line] (fixphon) -- (init);
				\path [line,dashed] (assumed) -- (fixphon);
				\path [line,dashed] (fixphon.east) --(fixphon.east-|assumed.east) |-(decide.east-|revised.north) -- (revised.north);
			\end{tikzpicture}}
		}
